---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SPECTRUM

<!-- badges: start -->
<!-- badges: end -->

The goal of SPECTRUM(Spatial Pattern Enhanced Cellular and Tissue Recognition Unified Method) is to combine inclusive prior known cell-type specific markers and spatial weighting for cell-type identification and spatial community detection.

## Installation

You can install the development version of SPECTRUM like so:

``` r
library(devtools)
devtools::install_github("WYucen/SPECTRUM")
```

## Example

This is a basic example that demonstrates how to perform cell type deconvolution using SPECTRUM:

```{r example}
library(SPECTRUM)

# Load example data
data("mob_demo_data")
markerList <- mob_demo_data$markerList
st_data <- mob_demo_data$st_mtx
position <- mob_demo_data$st_pos

# Set preprocessing parameters
minGene <- 100
minSpot <- 5

# Preprocess the spatial count matrix
st_data <- pre_process(st_data = st_data, minGene = minGene, minSpot = minSpot)
position <- position[colnames(st_data), ]  # Match position with filtered spots

# Plot Gabriel graph for spatial neighborhood structure
check_graph(position, data_struct = "dist", dist.th = 1.5, vertex.size = 1, ratio = 0.8)

# Perform deconvolution
pre_prop <- deconvo_process(
  st_data = st_data,
  location = position,
  data_struct = "dist",
  dist.th = 1.5,
  markerList = markerList
)

# Inspect result
head(pre_prop)

# Visualize deconvolution proportions
plot_ct(
  proportion = pre_prop,
  position = position,
  ct.select = colnames(pre_prop),
  NumCols = 5
)

# Visualize spatial cell type distribution with pie charts
plot_pie(
  proportion = pre_prop,
  position = position,
  cols = mob_demo_data$ct_cols
)
```

